A study on the usage of the wireless signal spectrum in a City of Things network

### 2017-05-26 advnetwpaper/5ghz_part.tex
Added too much. Removed validation from the part file

\begin{figure}[h!]
    \centering
    \textbf{cot-node6-student, channel 120, 12/05 - 20/05}\par\medskip
	\includegraphics[scale=0.5]{images/5_GHz/cot-node6-student_2017-05-20_chan64_image.pdf}
\end{figure}\\
which seems to show some traffic moving from channel 120 to channel 56 and / or 64 (TODO why doesnt it show on chan60?) on friday May 19th, which lasts all the way through saturday May 20th. We could not confirm when or if the signal ends due to the aforementioned (presumed) hardware failure. This signal still only amounts to an estimated signal strength of about -70 dBm which should still leave enough room for other traffic on the channel and in the spectrum.\\
For some nodes (all but cot-node6-student, cot-node8-student and node1), checking the higher up channels (the channels numbered 100 and above) shows no traffic on any of the nodes for those channels. For the three nodes mentioned, the fact that node1 shows some traffic on these channels is consistent with earlier observations of the outdoor node seeing more traffic on the 5 GHz band than the indoor nodes. For nodes cot-node6-student and cot-node8-student we don't have an explanation for why they have more traffic on these channels than the other nodes. Fact remains that the 100+ channels are relatively empty.
Included below are three graphs for three of our nodes; cot-node3-student, cot-node8-student and node1. Each of these was somewhat busy on the 2.4 GHz band, showed some traffic on the lower 5 GHz channels and demonstrates our findings for the higher channels:
\begin{figure}[h!]
    \centering
    \textbf{cot-node3-student, channel 100, 15/05 - 22/05}\par\medskip
	\includegraphics[scale=0.4]{images/5_GHz/cot-node3-student_2017-05-22_chan100_image.pdf}
\end{figure}\\
\begin{figure}[h!]
    \centering
    \textbf{cot-node12-student, channel 120, 12/05 - 16/05}\par\medskip
	\includegraphics[scale=0.4]{images/5_GHz/cot-node8-student_2017-05-16_chan120_image.pdf}
\end{figure}\\
\begin{figure}[h!]
    \centering
    \textbf{node1, channel 140, 13/05 - 17/05}\par\medskip
	\includegraphics[scale=0.4]{images/5_GHz/node1_2017-05-17_chan140_image.pdf}
\end{figure}\\
\subsection{Validation}
In terms of data validation, we have three parts that we looked at that give us confidence that our data would be valid.
scans met / zonder sturende laptop - stukje had gij al TODO

A second point is the discovering of daily patterns where we expected them. This includes the pattern of daily activity seen in the node at the Middelheim campus as well as seeing a decrease in activity on holidays such as May 1st TODO, we saw this on 12..
The third and final point that enforces our trust in the validity of the data we collected and thus also our findings is the fact that the outside node's measurements do not vary wildly from the indoor measurements: it's channel 6 and channel 11 activity is lower than it's channel 1 activity, which is the busiest channel. There is more jitter on the outdoor node's results which is most likely due to it being outside. Our measurements for channel 1 on the outside node can be found below:\\
\begin{figure}[h!]
    \centering
    \textbf{node1, channel 1, 13/05 - 17/05}\par\medskip
	\includegraphics[scale=0.5]{images/2_4_GHz/node1_2017-05-17_chan1_image.png}
\end{figure} \newpage

>>>>

\begin{figure}[h!]
    \centering
    \textbf{cot-node6-student, channel 120, 12/05 - 20/05}\par\medskip
	\includegraphics[scale=0.5]{images/5_GHz/cot-node6-student_2017-05-20_chan64_image.pdf}
\end{figure}\\
which seems to show some traffic moving from channel 120 to channel 56 and / or 64 (TODO why doesnt it show on chan60?) on friday May 19th, which lasts all the way through saturday May 20th. We could not confirm when or if the signal ends due to the aforementioned (presumed) hardware failure. This signal still only amounts to an estimated signal strength of about -70 dBm which should still leave enough room for other traffic on the channel and in the spectrum.\\
For some nodes (all but cot-node6-student, cot-node8-student and node1), checking the higher up channels (the channels numbered 100 and above) shows no traffic on any of the nodes for those channels. For the three nodes mentioned, the fact that node1 shows some traffic on these channels is consistent with earlier observations of the outdoor node seeing more traffic on the 5 GHz band than the indoor nodes. For nodes cot-node6-student and cot-node8-student we don't have an explanation for why they have more traffic on these channels than the other nodes. Fact remains that the 100+ channels are relatively empty.
Included below are three graphs for three of our nodes; cot-node3-student, cot-node8-student and node1. Each of these was somewhat busy on the 2.4 GHz band, showed some traffic on the lower 5 GHz channels and demonstrates our findings for the higher channels:
\begin{figure}[h!]
    \centering
    \textbf{cot-node3-student, channel 100, 15/05 - 22/05}\par\medskip
	\includegraphics[scale=0.4]{images/5_GHz/cot-node3-student_2017-05-22_chan100_image.pdf}
\end{figure}\\
\begin{figure}[h!]
    \centering
    \textbf{cot-node12-student, channel 120, 12/05 - 16/05}\par\medskip
	\includegraphics[scale=0.4]{images/5_GHz/cot-node8-student_2017-05-16_chan120_image.pdf}
\end{figure}\\
\begin{figure}[h!]
    \centering
    \textbf{node1, channel 140, 13/05 - 17/05}\par\medskip
	\includegraphics[scale=0.4]{images/5_GHz/node1_2017-05-17_chan140_image.pdf}
\end{figure}\\
